### 2020-03-13 Common/structure/info.tex
Julien and Johan: new model split figure
Julien and Johan: title

\thesistitle{Prostate Cancer Classification:\\A Freeze/Unfreeze Transfer Learning Approach Using Multiple Body Parts} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Prof. Dr. Philippe Cudré-Mauroux} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\cosupervisor{\href{https://exascale.info/members/giuseppe-cuccu/}{Dr. Giuseppe Cuccu},\\ \href{https://exascale.info/members/akansha/}{Akansha Bhardwaj}} % If you have a co-supervisor, include it here. This is used in the title page, print it elsewhere with \supname
\degree{Master} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{\href{mailto:julienclement22@gmail.com}{Julien Clément}\\ \href{mailto:joh.job13@gmail.com}{Johan Jobin}}% Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{Bd de Pérolles 90} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

>>>>

\thesistitle{Prostate Cancer Classification:\\A Transfer Learning Approach\\to Integrate Information\\From Diverse Body Parts} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Prof. Dr. Philippe Cudré-Mauroux} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\cosupervisor{\href{https://exascale.info/members/giuseppe-cuccu/}{Dr. Giuseppe Cuccu}\\ \href{https://exascale.info/members/akansha/}{Akansha Bhardwaj}} % If you have a co-supervisor, include it here. This is used in the title page, print it elsewhere with \supname
\degree{Master} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{\href{mailto:julienclement22@gmail.com}{Julien Clément}\\ \href{mailto:joh.job13@gmail.com}{Johan Jobin}}% Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{Bd de Pérolles 90} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname
